### 2018-08-29 Sections/a_new_frontier_towards_the_singularity.tex
Famous quotes

\dropcap{I}{n} this section we provide a non-technical outlook on the future quantum internet and its implications, for the benefit of the technically disinterested reader, who merely wishes to grasp some of the `big issues'. This section is in the form of several short essays, requiring no technical background knowledge in quantum computation, quantum mechanics, or mathematics.

>>>>

\dropcap{I}{n} this part we provide a non-technical outlook on the future quantum internet and its implications, for the benefit of the technically disinterested reader, who merely wishes to grasp some of the `big issues'. This section is in the form of several short essays, requiring no technical background knowledge in quantum computation, quantum mechanics, or mathematics.

### 2018-08-29 Sections/conclusion_the_vision_of_the_quantum_internet.tex
Added all dropcaps
Famous quotes

@@

Quantum technologies, particularly quantum computing, will truly revolutionise countless industries. With early demonstrations of key quantum technologies -- such as QKD, long distance quantum teleportation, and quantum computing -- becoming a reality, it is of utmost importance that networking protocols be pursued.

>>>>

\famousquote{When something is important enough, you do it even if the odds are not in your favour.}{Elon Musk}
\\
\\
\famousquote{Be nice to nerds. Chances are you’ll end up working for one.}{Bill Gates}
\\
\\
\famousquote{We are just an advanced breed of monkeys on a minor planet of a very average star. But we can understand the Universe. That makes us something very special.}{Stephen Hawking}

@@

\dropcap{Q}{uantum} technologies, particularly quantum computing, will truly revolutionise countless industries. With early demonstrations of key quantum technologies -- such as QKD, long distance quantum teleportation, and quantum computing -- becoming a reality, it is of utmost importance that networking protocols be pursued.
